Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-24 WRITEUP/ms.tex
annotation

% address the biggest MCC = molecular disk of \flower
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) and corresponds to the molecular disk of \flower (see also \Fig{vv}).
%
Thus, it encloses a large of stellar mass that is already assembled in \flower. The disk structure is excluded in the discussion of MCC dynamics in the remainder of this paper. \AP{minor mod: legend with horizontal alignment, text with arrows pointing to the disk and proper MMC clouds of points}
\label{fig:stellarRatio16}}
\end{figure}

>>>>

% address the biggest MCC = molecular disk of \flower
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
in the discussion of MCC dynamics in the remainder of this paper. 
\label{fig:stellarRatio16}}
\end{figure}
